Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone

### 2019-08-18 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

\DHKMchange{Let us consider an alternative cone, i.e.,
\begin{equation} \label{DHKM:altconedef}
    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\},
\end{equation}
where
$\norm[\calF']{f} =\norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk}}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}}$ and $\omega_{\bsk}$ decreases. The norm $\norm[\calF']{\cdot}$ is weaker than the norm $\norm[\calF]{\cdot}$, so this cone is defined as the subset of $\calF$ for which the weaker norm of the function  provides an upper bound the stronger norm of the function.  The following proposition describes the relationship between the cones defined in \eqref{DHKM:pilot_cone} and \eqref{DHKM:altconedef}.
\begin{proposition}
If there exist $A,A',A'', n_1,$ and $\boldsymbol{\omega}$ such that
\[\omega_{n_1} A'' \ge A \ge \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \text{ and} \qquad  \omega_{n_1+1}A' < 1, \]
then 
\[\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}
\subseteq 
\calC_{\boldsymbol{\lambda}, A}
\subseteq
\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}.\]
\end{proposition}

\begin{proof}
Let us prove $\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}
\subseteq 
\calC_{\boldsymbol{\lambda}, A}$ at first.
Suppose $f \in \calC_{\boldsymbol{\lambda}, A}$, then by definition we have
\begin{align*}
    \norm[\calF]{f} &\le A \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk = 1} ^{ n_1}}
     \le A \omega_{n_1}^{-1} \norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk}}{\lambda_{\bsk}} \right)_{\bsk =1} ^{n_1}}
     \le A \omega_{n_1}^{-1} \norm[\calF']{f}.
\end{align*}
Thus, if $A'' \ge A\omega_{n_1}^{-1}$, i.e. $\omega_{n_1} A'' \ge A $,
we obtain $\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$.

For the proof of the remaining part, 
suppose $f \in \calC'_{\boldsymbol{\lambda},\boldsymbol{\omega},  A'}$. Then we have
\begin{align*}
    \norm[\calF']{f}^\rho- \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho 
	& = \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho 
     \le \omega_{n_1+1}^\rho \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho \\
     & = \omega_{n_1+1}^\rho \left[ \norm[\calF]{f}^\rho - \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ]\\	
     & \le \omega_{n_1+1}^\rho \left[ A'{}^\rho \norm[\calF']{f}^\rho - \omega_1^{-\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ].
\end{align*}
Rearranging the terms, we obtain
\begin{align*}
\norm[\calF']{f}^\rho & \le \frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \\
 \iff	\norm[\calF]{f} & \le \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}.
\end{align*}
Hence, if $A \ge \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \text{ and } \omega_{n_1+1}A' < 1,$
we obtain $\calC_{\boldsymbol{\lambda}, A}
\subseteq
\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}.$
\end{proof}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tractability}\label{DHKM:SecPilotTract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\DHKMchange{
Besides understanding the dependence of $\COMP(\calA(\calC), \varepsilon,R)$ on $\varepsilon$, we also want to understand how $\COMP(\calA(\calC), \varepsilon,R)$ depends on the dimension of the domain of the input function.  Suppose that $f: \Omega^d \to \R$, for some $\Omega \subseteq \R$, and let $\calF_d$ denote the dependence of the input space on the dimension $d$.  
The set of functions for which our algorithms succeed, $\calC_d$, depends on the dimension, too.  Also, $\SOL$, $\APP$, $\COST$, and $\COMP$ depend implicitly on dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.

@@

\begin{itemize}   
\item We say that the adaptive approximation problem is strongly polynomially tractable
if and only if there are non-negative $C$, $p$, $\varepsilon_{\max}$, and $R_{\min}$ such that   
$$   
\COMP(\calA(\calC_d), \varepsilon,R)\le C\,R^p\,\varepsilon^{-p} \qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
$$   
The infimum of $p$ satisfying the bound above is denoted by $p^*$   
and is called the exponent of strong polynomial tractability.    
\newline \qquad

\item    
We say that the problem is polynomially tractable
if and only if there are non-negative $C,p$, $q$,  $\varepsilon_{\max}$, and $R_{\min}$ such that   
$$   
\COMP(\calA(\calC_d), \varepsilon,R)\le C\,d^{\,q}\,R^p\,   
\varepsilon^{-p}\qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).  
$$   
\vskip 0.5pc

@@

Necessary and sufficient conditions on these tractability notions will be studied 
for different types of algorithms in Sections \ref{DHKM:SecPilotTract} and \ref{DHKM:SecDecayTract}.

@@

Recall that we assume that 
$\lambda_{d,\bsk_1}\ge \lambda_{d,\bsk_2}\ge \cdots >0$. Let 
\[
n(\delta,d) :=\min \left \{n\ge 0: \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
    \le \delta \right \} \qquad \forall \delta > 0.
\]
From 
Equations \eqref{DHKM:PilotConeAlg_cost} and \eqref{DHKM:PilotConeAlg_comp}, we obtain that 
\begin{multline*}
     \COMP(\calA(\calC_d),\omega_{\textup{lo}} \varepsilon,R) \le n(\varepsilon/R,d) \le 
        \COMP(\calA(\calC_d),\omega_{\textup{hi}} \varepsilon,R)  \\
        \forall \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty),
\end{multline*}
where the positive constants $\omega_{\textup{lo}}$ and $\omega_{\textup{hi}}$  depend on $A$, but not depend on $d$, $\varepsilon$, or $R$.  From the equation above, it is clear that tractability depends on the behavior of $n(\varepsilon/R,d)$ as $R/\varepsilon$ and $d$ tend to infinity. We would like to study under which conditions we obtain the various tractability notions defined above

@@

\begin{theorem} \label{DHKM:thmtract1}
Using the same notation as above, the following statements hold for the case $\rho'=\infty$.
 \begin{itemize}
  \item[1.] 
  We have strong polynomial tractability if and only if there exist $\eta>0$ and $i_0\in\NN$ such that
 \begin{equation}\label{DHKM:eq:condspt}
    \sup_{d\in\NN} \sum_{i=i_0}^\infty \lambda_{d,\bsk_i}^\eta < \infty.
 \end{equation}
 Furthermore, the exponent of strong polynomial tractability is then equal to the infimum of those $\eta>0$ for which \eqref{DHKM:eq:condspt} holds. 
 \item[2.] 
  We have polynomial tractability if and only if there exist $\eta_1, p_2 \ge 0$ and $\eta_3, K>0$ such that
 \[
    \sup_{d\in\NN} d^{-\eta_1}\, \sum_{i=\lceil K d^{\eta_2} \rceil}^\infty \lambda_{d,\bsk_i}^{\eta_3} < \infty.
 \]
 \item[3.] 
 We have weak tractability if and only if 
 \begin{equation}\label{DHKM:eq:condwt}
  \sup_{d\in\NN} \, \exp(-cd) \sum_{i=1}^\infty \exp\left(-c\left(\frac{1}{\lambda_{d,\bsk_i}}\right)\right) <\infty\quad \mbox{for all}\quad c>0.
 \end{equation}
\end{itemize}
\end{theorem}

@@

Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $\SOL(f)$, to decay monotonically. However, we expect their partial sums to decay steadily.  The series coefficients for wavenumbers $\bsk \in \calK_0$ do not affect the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ and may behave erratically.
Lemma \ref{DHKM:Key_Lem} implies that 
\begin{equation} \label{DHKM:LambdaDef}
    \norm[\tau]{\bigl(\hf(\bsk) \bigr)_{\bsk \in \calK_j}} \le \sigma_j(f) \Lambda_j, \qquad \text{where } \Lambda_j : = \norm[\rho']{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}}.
\end{equation}
From \eqref{DHKM:SOLNorm} and \eqref{DHKM:SOLNormFinite} it follows that the norm of the solution operator is 
\begin{equation} \label{DHKM:NormLambdaFinite}
    \norm[\calF \to \calG]{\SOL} = \bignorm[\rho']{\bigl(\Lambda_j \bigr)_{j \in \N_0}} < \infty
\end{equation}

If $f$ belongs to the $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ defined in \eqref{DHKM:TrackConeDef} and $n_0 = 0$, then 
\begin{align*}
    \norm[\calF]{f} & = \norm[\rho]{\Biggl(\,\norm[\rho]{\biggl(\frac{\hf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}}\,\Biggr)_{j \in \N}} = \bignorm[\rho]{\bigl(\sigma_j(f) \bigr)_{j \in \N}} \\
    & \le \bignorm[\rho]{\bigl(\sigma_1(f), ab \sigma_1(f), ab^2 \sigma_1(f), \ldots \bigr)} \\
    & = \left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}  \norm[\rho]{\biggl(\frac{\hf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_1}}.
\end{align*}
Comparing this inequality to the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ in the previous section, it can be seen that $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $  defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} $defined in \eqref{DHKM:pilot_cone} if we choose 
$A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.

>>>>

\DHKMchange{Our $\calC_{\boldsymbol{\lambda},n_1,A}$ is a cone for which a pilot sample of the input function allows you to bound its norm.  An alternative might be to define a cone for which a weaker norm of the function provides an upper bound on the original norm.  Here is such a cone:
\begin{multline} \label{DHKM:altconedef}
    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}:=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\}, \\ \text{where } \norm[\calF']{f} :=\norm[\rho]{\left( \frac{\hf(\bsk)\omega_{i}}{\lambda_{\bsk}} \right)_{i =  1}^n} \text{ and } \omega_1 \ge \omega_2 \ge \cdots.
\end{multline}
The norm $\norm[\calF']{\cdot}$ is weaker than the norm $\norm[\calF]{\cdot}$, so this cone is a strict subset of $\calF$.  The following proposition describes how the cones defined in \eqref{DHKM:pilot_cone} and \eqref{DHKM:altconedef} are related.
\begin{proposition}
If the parameters $A,A',A'', n_1,$ and $\boldsymbol{\omega}$ satisfy
\[ 
\omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho}
\le A \le \omega_{n_1} A'' \text{ and} \qquad  \omega_{n_1+1}A' < 1, 
\]
then 
\[
\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}
\subseteq 
\calC_{\boldsymbol{\lambda}, n_1, A}
\subseteq
\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}.
\]
\end{proposition}

\begin{proof}
Let us prove $
\calC_{\boldsymbol{\lambda}, A} \subseteq \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$ first.
Suppose $f \in \calC_{\boldsymbol{\lambda}, n_1, A}$, then by the definition of $\calC_{\boldsymbol{\lambda}, n_1, A}$ we have
\begin{equation*}
    \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i = 1} ^{ n_1}}
     \le A \omega_{n_1}^{-1} \norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk_i}}{\lambda_{\bsk_i}} \right)_{i =1} ^{n_1}}
     \le A \omega_{n_1}^{-1} \norm[\calF']{f}.
\end{equation*}
Thus, if $A\omega_{n_1}^{-1} \le A''$, i.e. $A \le \omega_{n_1} A'' $, then
we obtain $f \in \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$.  So,

For the proof that 
$\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}
\subseteq 
\calC_{\boldsymbol{\lambda}, n_1, A}$, 
suppose $f \in \calC'_{\boldsymbol{\lambda},\boldsymbol{\omega},  A'}$. Then we have
\begin{align*}
    \norm[\calF']{f}^\rho- \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho 
	& = \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho 
     \le \omega_{n_1+1}^\rho \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho \\
     & = \omega_{n_1+1}^\rho \left[ \norm[\calF]{f}^\rho - \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ]\\	
     & \le \omega_{n_1+1}^\rho \left[ A'{}^\rho \norm[\calF']{f}^\rho - \omega_1^{-\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ].
\end{align*}
Assuming $\omega_{n_1+1}A' < 1$ and rearranging the above terms, we obtain
\begin{align*}
\norm[\calF']{f}^\rho & \le \frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \\
	\norm[\calF]{f} & \le \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}.
\end{align*}
Hence, if $\omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \le A$, it follows that $f \in \calC_{\boldsymbol{\lambda}, n_1, A}$ and so
we obtain $
\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}
\subseteq
\calC_{\boldsymbol{\lambda}, n_1, A}
$.
\end{proof}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Tractability}\label{DHKM:SecPilotTract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\DHKMchange{
Besides understanding the dependence of $\COMP(\calA(\calC), \varepsilon,R)$ on $\varepsilon$, we also want to understand how $\COMP(\calA(\calC), \varepsilon,R)$ depends on the dimension of the domain of the input function.  Suppose that $f: \Omega^d \to \R$, for some $\Omega \subseteq \R$, and let $\calF_d$ denote the dependence of the input space on the dimension $d$.  
The set of functions for which our algorithms succeed, $\calC_d$, depends on the dimension, too.  Also, $\SOL$, $\APP$, $\COST$, and $\COMP$ depend implicitly on the dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.

@@

\begin{itemize}   
\item We say that the adaptive approximation problem is strongly polynomially tractable
if and only if there are non-negative $C$, $p$, and positive $\varepsilon_{\max}$, and $R_{\min}$ such that   
$$   
\COMP(\calA(\calC_d), \varepsilon,R)\le C\,R^p\,\varepsilon^{-p} \qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
$$   
The infimum of $p$ satisfying the bound above is denoted by $p^*$   
and is called the exponent of strong polynomial tractability.    
\newline \qquad

\item    
We say that the problem is polynomially tractable
if and only if there are non-negative $C,p$, $q$, and positive $\varepsilon_{\max}$, and $R_{\min}$ such that   
$$   
\COMP(\calA(\calC_d), \varepsilon,R)\le C\,d^{\,q}\,R^p\,   
\varepsilon^{-p}\qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).  
$$   
\vskip 0.5pc

@@

Necessary and sufficient conditions on these tractability notions will be studied 
for different types of algorithms in this section and Section \ref{DHKM:SecDecayTract}.

@@

Recall that we assume that 
$\lambda_{d,\bsk_1}\ge \lambda_{d,\bsk_2}\ge \cdots >0$. Let 
\[
n(\delta,d) :=\min \left \{n\ge 0: \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
    \le \delta \right \} \qquad \forall \delta > 0.
\]
From 
Equations \eqref{DHKM:PilotConeAlg_cost} and \eqref{DHKM:PilotConeAlg_comp}, we obtain that 
\begin{multline*}
     \COMP(\calA(\calC_d),\omega_{\textup{lo}} \varepsilon,R) \le n(\varepsilon/R,d) \le 
        \COMP(\calA(\calC_d),\omega_{\textup{hi}} \varepsilon,R)  \\
        \forall \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty),
\end{multline*}
where the positive constants $\omega_{\textup{lo}}$ and $\omega_{\textup{hi}}$  depend on $A$, but do not depend on $d$, $\varepsilon$, or $R$.  From the equation above, it is clear that tractability depends on the behavior of $n(\varepsilon/R,d)$ as $R/\varepsilon$ and $d$ tend to infinity. We would like to study under which conditions we obtain the various tractability notions defined above.

@@

\begin{theorem} \label{DHKM:thmtract1}
Using the same notation as above, the following statements hold for the case $\rho'=\infty$.
 \begin{itemize}
  \item[1.] 
  We have strong polynomial tractability if and only if there exist $\eta>0$ and $i_0\in\NN$ such that
 \begin{equation}\label{DHKM:eq:condspt}
    \sup_{d\in\NN} \sum_{i=i_0}^\infty \lambda_{d,\bsk_i}^\eta < \infty.
 \end{equation}
 Furthermore, the exponent of strong polynomial tractability is then equal to the infimum of those $\eta>0$ for which \eqref{DHKM:eq:condspt} holds. 
 \item[2.] 
  We have polynomial tractability if and only if there exist $\eta_1, \eta_2 \ge 0$ and $\eta_3, K>0$ such that
 \[
    \sup_{d\in\NN} d^{-\eta_1}\, \sum_{i=\lceil K d^{\eta_2} \rceil}^\infty \lambda_{d,\bsk_i}^{\eta_3} < \infty.
 \]
 \item[3.] 
 We have weak tractability if and only if 
 \begin{equation}\label{DHKM:eq:condwt}
  \sup_{d\in\NN} \, \exp(-cd) \sum_{i=1}^\infty \exp\left(-c\left(\frac{1}{\lambda_{d,\bsk_i}}\right)\right) <\infty\quad \mbox{for all}\quad c>0.
 \end{equation}
\end{itemize}
\end{theorem}

@@

Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $\SOL(f)$, to decay monotonically. However, we expect their partial sums to decay steadily.  The series coefficients for wavenumbers $\bsk \in \calK_0$ do not affect the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ and may behave erratically.
Lemma \ref{DHKM:Key_Lem} implies that 
\begin{equation} \label{DHKM:LambdaDef}
    \norm[\tau]{\bigl(\hf(\bsk) \bigr)_{\bsk \in \calK_j}} \le \sigma_j(f) \Lambda_j, \qquad \text{where } \Lambda_j : = \norm[\rho']{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}}.
\end{equation}
From \eqref{DHKM:SOLNorm} and \eqref{DHKM:SOLNormFinite} it follows that the norm of the solution operator is 
\begin{equation} \label{DHKM:NormLambdaFinite}
    \norm[\calF \to \calG]{\SOL} = \bignorm[\rho']{\bigl(\Lambda_j \bigr)_{j \in \N_0}} < \infty.
\end{equation}

If $f$ belongs to the $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ defined in \eqref{DHKM:TrackConeDef} and $n_0 = 0$, then 
\begin{align*}
    \norm[\calF]{f} & = \norm[\rho]{\Biggl(\,\norm[\rho]{\biggl(\frac{\hf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}}\,\Biggr)_{j \in \N}} = \bignorm[\rho]{\bigl(\sigma_j(f) \bigr)_{j \in \N}} \\
    & \le \bignorm[\rho]{\bigl(\sigma_1(f), ab \sigma_1(f), ab^2 \sigma_1(f), \ldots \bigr)} \\
    & = \left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}  \norm[\rho]{\biggl(\frac{\hf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_1}}.
\end{align*}
Comparing this inequality to the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} $ in the previous section, it can be seen that $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $  defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone} if we choose 
$A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
